---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, 
  results = 'hold',
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Repository for R package afedR3 

Includes several functions related to the third edition of book "Analyzing Financial and Economic Data with R", available in the following formats:

- [Amazon](https://www.amazon.com/dp/B084LSNXMN) - full length book
- [Online version](https://www.msperlin.com/afedR/) - first seven chapters


## Installation

```
# only in github
devtools::install_github('msperlin/afedR3')
```

## Example of usage

### Listing available datasets

```{r}
afedR3::data_list()
```

### Fetching data from book repository

```{r}
file_name <- 'CH04_SP500.csv'
path_to_file <- afedR3::data_path(file_name)

df <- readr::read_csv(path_to_file)
dplyr::glimpse(df)
```

### Copying all book files to local directory

```{r}
temp_path <- fs::path_temp('afedR3')

flag <- afedR3::bookfiles_get(path_to_copy = temp_path)
```

