```{r solution, echo = FALSE, results = "hide"}
library(dplyr)

first_date <- '2015-01-01'
last_date <- '2023-01-01'

df_prices <- yfR::yf_get('GOOG', 
                         first_date,
                         last_date)

value_purchase <- sample(seq(1000, 10000, by = 50), 1)

# solution
my_sol <- last(df_prices$price_adjusted)/first(df_prices$price_adjusted)*value_purchase
```

```{r datageneration, echo = FALSE, results = "hide"}
my_answers <- afedR3::format_cash(
  as.numeric(afedR3::make_random_answers(my_sol)))

#check_answers(my_answers)
```


Question
========

Use the `yfR` package to download Google (GOOG) stock data, from `r first_date` to `r last_date`. If the investor had bought 1000 USD in Google shares on the first day of the data and kept the investment until today, what would be the value of his portfolio?

```{r questionlist, echo = FALSE, results = "asis"}
exams::answerlist(my_answers, markup = "markdown")
```

Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: schoice
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "yfR"
exshuffle: TRUE

