```{r solution, echo = FALSE, results = "hide", message=FALSE, eval=FALSE}
library(dplyr)

my_f <-  afedR3::data_path('CH11_grunfeld.csv')

df_grunfeld <- readr::read_csv(my_f, col_types = readr::cols())

my_tab <- tibble(nrows = nrow(df_grunfeld),
                 ncol = ncol(df_grunfeld),
                 n_companies = length(unique(df_grunfeld$firm)),
                 n_years = length(unique(df_grunfeld$year)))

my_tab

library(xtable)

# Save to lates
# save to temp file
my_tex_file <- tempfile(pattern = 'table', fileext = '.tex')
print(xtable(my_tab), file = my_tex_file)

readr::read_lines(my_tex_file)
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
#my_answers <- make_random_answers(my_sol)
my_answers <- rep(NA, 5)

type_question <- 'string'
ex_name <- 'reporting 12 01'

my_f <-  afedR3::data_path('CH11_grunfeld.csv')

```

Question
========

Using package `afedR3`, import the data from file `r basename(my_f)` and create a descriptive table of the variables. This table should provide enough information for the reader to understand the data. Use `xtable` package to report it in _LaTeX_ or Word/Writer format.



Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: `r type_question`
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: `r ex_name`
exshuffle: TRUE

