```{r solution, echo = FALSE, results = "hide", message=FALSE, eval=FALSE}
library(dplyr)

tickers <- sample(yfR::yf_index_composition("SP500")$ticker, 4)
first_date <- Sys.Date() - 3*365
last_date  <- Sys.Date()

df_stocks <- yfR::yf_get(tickers, 
                         first_date, 
                         last_date)

my_tab <- df_stocks |>
  na.omit() |>
  group_by(ticker) |>
  do(my_arima = arima(x = .$ret_adjusted_prices, 
                      order = c(1, 0, 1))) 

glimpse(my_tab)

# solution
library(texreg)

screenreg(my_tab$my_arima)
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
#my_answers <- make_random_answers(my_sol)
my_answers <- rep(NA, 5)

type_question <- 'string'
ex_name <- 'reporting 12-02'
```

Question
========

Using the `BatchGetSymbols::GetSP500Stocks` function, select 4 stocks at random and download the adjusted price data for the last three years. Estimate an ARIMA(1, 0, 1) model for each stock and report the result on the R screen with the `texreg::screenreg` function.


Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: `r type_question`
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: `r ex_name`
exshuffle: TRUE

