```{r solution, echo = FALSE, results = "hide", message=FALSE, eval=FALSE}
library(yfR)
library(dplyr)
library(readr)
library(stringr)
library(ggplot2)

df_prices <- yfR::yf_collection_get(
  'DOW',
  first_date = '2015-01-01',
  freq_data = 'yearly'
  )

tab <- df_prices |>
  na.omit() |>
  group_by(ticker) |>
  summarise(mean = mean(ret_adjusted_prices),
            sd = sd(ret_adjusted_prices))

p <- ggplot(tab, aes(x = sd, y = mean)) + 
  geom_point() + 
  xlim(0, 0.5) + ylim(-0.5, 0.5)

print(p)
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
my_answers <- rep(0, 5)
```

Question
========

Use the `yfR::yf_collection_get()` function to download the **annual** return data for all stocks in the DOW index, from `r '2015-01-01'` to the current day. After that, create the average/variance map by plotting the average **annual* return as the y axis and the standard deviation as the x axis. Tip: You'll find many outliers in the raw data. Make sure that the graph is visible limiting the x and y axes (see the `ggplot2::xlim` and `ggplot2::ylim` functions).


Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: string
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "function 01"
exshuffle: TRUE

