```{r solution, echo = FALSE, results = "hide", message=FALSE, eval=FALSE}
library(yfR)
library(ggplot2)

tickers <- c('AAPL', 
             'MSFT',
             'AMZN',
             'GOOG') 

df_stocks <- yf_get(
     tickers = tickers, 
     first_date = Sys.Date() - 500,
     last_date = Sys.Date()
     )

p <- ggplot(df_stocks, aes(x = ref_date, 
                           y = price_adjusted,
                           color = ticker)) + 
  geom_line() + 
  labs(title = paste0('Prices for ', tickers) ,
       subtitle = paste0('Data from ', min(df_stocks$ref_date), ' to ', 
                         max(df_stocks$ref_date)),
       caption = "Solution for exercise 02, chapter 10 - afedR")

print(p)
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
my_answers <- rep(0, 5)
```

Question
========

Using the `yfR` package, download stock data for:

- APPLE INC. (AAPL)
- MICROSOFT CORPORATION	(MSFT)
- AMAZON.COM, INC.	(AMZN)
- ALPHABET INC. (GOOG)
  
in the last 1500 days. Display stock prices with different line colors on the same graph. Adapt all other aspects of the graph from previous exercises such as title and axis labels.


Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: string
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "function 01"
exshuffle: TRUE

