```{r solution, echo = FALSE, results = "hide", message=FALSE, eval=FALSE}
library(yfR)
library(ggplot2)

tickers <- 'TLSA'

df_tlsa<- yf_get(tickers = tickers, 
                 first_date = Sys.Date() - 500,
                 last_date = Sys.Date())

p <- ggplot(df_tlsa, aes(x = ref_date, y = price_adjusted)) + 
  geom_line() + 
  labs(title = paste0('Prices for ', tickers) ,
       subtitle = paste0('Data from ', min(df_tlsa$ref_date), ' to ', 
                         max(df_tlsa$ref_date)),
       caption = "Solution for exercise 01, chapter 10 - afedR")

print(p)
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
my_answers <- rep(0, 5)
```

Question
========

Download TESLA (TSLA) stock data with the `yfR` package for the last 500 days. Display the price line chart adjusted over time using the `r afedR3::format_fct_text("ggplot")` function. Make sure that:

- x and y axes are correctly named;
- The chart has a title ("Prices for TESLA"), subtitle ("Data from YYYY-MM-DD to YYYY-MM-DD") and a _caption_ ("Solution for exercise 01, chapter 10 - afedR").



Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: string
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "function 01"
exshuffle: TRUE

