```{r solution, echo = FALSE, results = "hide", message=FALSE}
ticker <- '^FTSE'

first_date <- '2010-01-01'
last_date <- '2021-01-01'

df_FTSE_daily <- yfR::yf_get(ticker,
                            first_date,
                            last_date)

# change from daily to annual
df_FTSE_yearly <- df_FTSE_daily %>%
  mutate(ref_year = lubridate::year(ref_date)) %>%
  group_by(ref_year) %>%
  summarise_all(.funs = last)

print(df_FTSE_yearly)
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
my_answers <- rep(NA, 5)
```

Question
========

Use the `yfR::yf_get` function to import  the prices of the FTSE index (`'^ FTSE'`) from `r first_date` to `r last_date`. Then, reconstruct the data at the annual frequency, defining each year's value as the last observation of the period. Tip: see the `dplyr::summary_all` function for a functional way to aggregate all the columns of a `dataframe`.


Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: string
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "function 01"
exshuffle: TRUE

