```{r solution, echo = FALSE, results = "hide"}
my_f <- afedR3::data_path("CH04_another-funky-csv-file.csv")

df_funky <- read.table(file = my_f, 
           dec = '?', 
           skip = 7, 
           sep = '|', 
           header = TRUE)

my_sol <- nrow(df_funky) + ncol(df_funky)
```

```{r datageneration, echo = FALSE, results = "hide"}
my_answer <- afedR3::make_random_answers(my_sol)

afedR3::check_answers(my_answer)
```

Question
========

In the book package there is a data file called `r basename(my_f)`. This has a particularly bizarre format for the data. Open it in a text editor and try to understand how the columns are separated and what is symbol for decimals. After that, study the inputs of function `read.table` and import the table into your R  session. If we add the number of rows to the number of columns in the imported table, what is the result?


Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: num
exsolution: `r my_sol`
exname: "funky file"
exshuffle: TRUE

