```{r solution, echo = FALSE, results = "hide", message=FALSE, eval=FALSE}
library(ggplot2)

tickers <- yfR::yf_index_composition("DOW")$ticker
first_date <- Sys.Date() - 3*365
last_date  <- Sys.Date()

df_stocks <- yfR::yf_get(tickers, 
                         first_date, 
                         last_date)

df_sp500 <- yfR::yf_get('^GSPC', 
                        first_date, 
                        last_date)

idx <- match(df_stocks$ref_date, df_sp500$ref_date)
df_stocks$ret_mkt <- df_sp500$ret_closing_prices[idx]

# calculate beta for each stock
estimate_beta <- function(df) {
  # Function to estimate beta from dataframe of stocks returns
  #
  # Args:
  #   df - Dataframe with columns ret and ret.sp500
  #
  # Returns:
  #   The value of beta
  
  my_model <- lm(data = df, 
                 formula = ret_adjusted_prices ~ ret_mkt)
  
  return(coef(my_model)[2])
}

my_betas <- by(data = df_stocks, 
               INDICES = df_stocks$ticker, 
               FUN = estimate_beta)

glimpse(my_betas)

# solution
p <- ggplot(tibble::tibble(betas = my_betas), aes(x = betas)) + 
  geom_histogram()

print(p)
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
#my_answers <- afedR3::make_random_answers(my_sol)
my_answers <- rep(NA, 5)

type_question <- 'string'
ex_name <- 'models 11 04'
```

Question
========

Use command `yfR::yf_index_composition("DOW")` to find the ticker of the components of the index and `yfR::yf_get` to download all available price data. Using the SP500 itself -- ticker `'^GSPC'` -- as the market index, calculate the beta for all stocks. Display the histogram of the estimated _betas_. Note that the SP500 returns are not available in the original database and must be downloaded and added to the original database.


Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: `r type_question`
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: `r ex_name`
exshuffle: TRUE

