```{r solution, echo = FALSE, results = "hide", message=FALSE, eval=FALSE}
library(dplyr)

tickers <- yfR::yf_index_composition("DOW")$ticker
first_date <- Sys.Date() - 3*365
last_date  <- Sys.Date()

df_stocks <- yfR::yf_get(tickers, 
                         first_date, 
                         last_date)

df_sp500 <- yfR::yf_get('^GSPC', 
                        first_date, 
                        last_date)

my_tab <- df_stocks |>
  group_by(ticker) |>
  do(my_arima = arima(x = .$ret_adjusted_prices, 
                      order = c(1,0,0))) |>
  mutate(arima_forecast = predict(my_arima, n.ahead = 1 )$pred[1])

glimpse(my_tab)

# solution
idx <- which.max(my_tab$arima_forecast )
print(my_tab$ticker[idx])
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
#my_answers <- afedR3::make_random_answers(my_sol)
my_answers <- rep(NA, 5)
```

Question
========

Using the tidyverse functions, `dplyr::group_by` and `dplyr::do`, estimate an ARIMA model for the returns of each stock, available from the import process of previous exercise. In the same output dataframe, create a new column with the forecast in _t + 1_ for each model. Which stock has the highest expected return for _t + 1_?


Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: string
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "function 01"
exshuffle: TRUE

